### 2017-12-02 1/exams/m1.tex

\documentclass[12pt]{article}
\usepackage{fullpage}
\usepackage{times}
\usepackage{xcolor,censor}
\usepackage{fancyvrb}

@@

\vskip 2.5in

\begin{SaveVerbatim}{VerbEnv}  
SOLUTION:
\end{SaveVerbatim}

@@

@@

;; dist3d : 3D -> Number
;; Compute distance to origin from given 3-d point
(check-expect (dist3d (make-3d 3 2 6)) 7)
(define (dist3d p)
  (sqrt (+ (sqr (3d-x p)) (sqr (3d-y p)) (sqr (3d-z p)))))  
\end{SaveVerbatim}

@@

>>>>

\documentclass[12pt]{article}
\usepackage{fullpage}
\usepackage{times}
\usepackage{xcolor,censor}
\usepackage{fontspec}
\usepackage{fancyvrb}

\setmainfont{Times New Roman}

@@

(cond [(w 2) 4] [else 9])     -->[plug]
       ^^^^^
(cond [(= R 2) 4] [else 9])   -->[const]
          ^
(cond [(= 9 2) 4] [else 9])   -->[arith]
       ^^^^^^^
(cond [#false 4] [else 9])    -->[cond]
^^^^^^^^^^^^^^^^^^^^^^^^^^
(cond [else 9])               -->[cond]
^^^^^^^^^^^^^^^
9
\end{SaveVerbatim}

@@

\begin{SaveVerbatim}{VerbEnv}  
SOLUTION:

- make-run  : Constructor
- run-time  : Accessor
- run-up    : Accessor
- run-score : Accessor
- run?      : Predicate
\end{SaveVerbatim}

@@

(check-expect (name-width (make-name "Bob" "Harper")) 100)
(check-expect (name-width (make-name "Bo" "Jack")) 70)
(define (name-width n)
  (* 10 (+ 1 (string-length (name-first n))
             (string-length (name-last n)))))
\end{SaveVerbatim}

@@

;; count : LoN -> Number
;; Count the number of non-negative numbers in list
(check-expect (count-non-neg '()) 0)
(check-expect (count-non-neg (list 1 -2 8 0)) 3)
(define (count-non-neg lon)
  (cond [(empty? lon) 0]
        [(cons? lon)
         (if (< (first lon) 0)
             (count-non-neg (rest lon))
             (add1 (count-non-neg (rest lon))))]))
\end{SaveVerbatim}
